The problem and promise of scale in multilayer networks

### 2020-01-31 paper/manuscript.Rmd
Update manuscript.Rmd

In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks represent continuous and simultaneous movement trajectories of animals. Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale (global migration: Flack et al. 2018). Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g. Muller et al. 2018; Finn et al. 2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019). Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).

@@

We thank all members of the Wildlife Evolutionary Ecology Lab, including K. Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, and L. Newediuk for their comments on previous versions of this manuscript as well as D. Schneider for inspiration and helpful discussions about scale. Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.

>>>>

In contrast to spatial networks, where nodes represent spatial locations that are fixed in space, movement networks can represent continuous and simultaneous movement trajectories of multiple animals. Continuous collection of animal relocation data using GPS technology can be used to measure how groups of animals make collective movement decisions in the context of their local environment (Strandburg-Peshkin et al. 2015, 2017) and across scales. A collective movement layer could constitute similarity in movement for dyads (Long et al. 2014) or groups (Bode et al. 2011). This movement layer could be made at a fine (i.e. minute-to-minute: Cleasby et al. 2019) or coarse scale (global migration: Flack et al. 2018). Another potential application would be to generate social networks during times when animals are engaged in different behaviours, including traveling, interacting, or foraging (e.g. Muller et al. 2018; Finn et al. 2019) and construct a multilayer network based on behaviour-specific monolayer networks (e.g. Smith-Aguilar et al. 2019). Importantly, the key to incorporating movement in multilayer networks across scales is the technological advancements available to overcome previous limitations (see Hughey et al. 2018).

@@

We thank all members of the Wildlife Evolutionary Ecology Lab, including K. Kingdon, S. Boyle,  C. Prokopenko, I. Richmond, J. Hogg, and L. Newediuk for their comments on previous versions of this manuscript as well as D. Schneider for inspiration and helpful discussions about scale. Funding for this study was provided by a Vanier Canada Graduate Scholarship to QMRW and a NSERC Discovery Grant to EVW.
